%The Arborec

\newcommand{\letaniI}{
\name{Letani Warrior Infantry I}\\
Cost 1(2) |  Combat 8\\
\emph{Production} 1
}

\newcommand{\letaniII}{
\name{Letani Warrior Infantry II (GG)}\\
Cost 1(2) | Combat 7\\
\emph{Production} 2\\
After this unit is destroyed, roll 1 die. If the result is 6 or greater, place the unit on this card. At the start of your next turn, place units from the card on a planet you control in your home system.
}

\newcommand{\bioplasmosis}{
\name{Bioplasmosis (GG)}{green}\\
At the end of the status phase, you may remove
any number of infantry from planets you control
and place them on 1 or more planets you control
in the same or adjacent systems.
}

%The Argent Flight

\newcommand{\strikeWingI}{
\name{Strike Wing Alpha Destroyer I}\\
Cost 1 | Combat 8 | Move 2 | Capacity 1 \\
\emph{Anti-Fighter Barrage} 9x2
}

\newcommand{\strikeWingII}{
\name{Strike Wing Alpha Destroyer II (RR)}\\
Cost 1 | Combat 7 | Move 2 | Capacity 1 \\
\emph{Anti-Fighter Barrage} 6x3 \\
When this unit uses \emph{Anti-Fighter Barrage} each result of 9 or 10 also destroys 1 of your opponent's infantry in the space area of the active system.
}

\newcommand{\hololattice}{
\name{Aerie Hololattice (Y)}{yellow}\\
Other players cannot move ships through systems that contain your structures.
Each planet that contains 1 or more of your structures gains the \emph{Production} 1 ability as if it were a unit.
}

%The Barony of Letnev

\newcommand{\disruptors}{
\name{L4 Disruptors (Y)}{yellow}\\
During an invasion, units cannot use Space Cannon
against your units.
}

\newcommand{\NES}{
\name{Non-Euclidean Shielding (RR)}{red}\\
When one of your units uses \emph{Sustain Damage},
cancel 2 hits instead of 1.
}

%The Clan of Saar

\newcommand{\factoryI}{
\name{Floating Factory I}\\
Move 1 | Capacity 4 | \emph{Production} 5\\
This unit is placed in a space area instead of on a
planet. This unit can move and retreat as if it were
a ship. If this unit is blockaded, it is destroyed.
}

\newcommand{\factoryII}{
\name{Floating Factory II (YY)}\\
Move 2 | Capacity 5 | \emph{Production} 7\\
This unit is placed in a space area instead of on a
planet. This unit can move and retreat as if it were
a ship. If this unit is blockaded, it is destroyed.
}

\newcommand{\chaosMapping}{
\name{Chaos Mapping (B)}{blue}\\
Other players cannot activate asteroid fields that
contain 1 or more of your ships.
At the start of your turn during the action phase,
you may produce 1 unit in a system that contains
at least 1 of your units that has \emph{Production}.
}

%The Council Keleres

\newcommand{\iihq}{
\name{I.I.H.Q. Modernization (Y)}{yellow}\\
You are neighbors with all players that have units or control planets in or adjacent to the Mecatol Rex system.\\
Gain the Custodia Vigilia planet card and its legendary planet ability card. You cannot lose these cards, and this card cannot have an X or Y assimilator token placed on it.\\
\vspace{5pt}\\
\custodia
}

\newcommand{\asn}{
\name{Agency Supply Network (YY)}{yellow}\\
Whenever you resolve one of your \emph{Production} abilities, you may resolve an additional one of your \emph{Production} abilities in any system; the additional use does not trigger this ability.
}

%The Embers of Muaat

\newcommand{\prototypeI}{
\name{Prototype War Sun I}\\
Cost 12 | Combat 3x3 | Move 1 | Capacity 6\\
\emph{Sustain Damage}\\
\emph{Bombard} 3x3\\
Other players' units lose \emph{Planetary Shield}.
}

\newcommand{\prototypeII}{
\name{Prototype War Sun II (RRRY)}\\
Cost 10 | Combat 3x3 | Move 3 | Capacity 6\\
\emph{Sustain Damage}\\
\emph{Bombard} 3x3\\
Other players' units lose \emph{Planetary Shield}.
}

\newcommand{\magmus}{
\name{Magmus Reactor (RR)}{red}\\
Your ships can move into supernovas.\\
Each supernova that contains 1 or more of your units gains the \emph{Production} 5 ability as if it were 1 of your units.
}

%The Emirates of Hacan

\newcommand{\biomes}{
\name{Production Biomes (GG)}{green}\\
\emph{Action:}
Exhaust this card and spend 1 token from
your strategy pool to gain 4 trade goods and
choose 1 other player, he gains 2 trade goods.
}

\newcommand{\datahub}{
\name{Quantum Datahub Node (YYY)}{yellow}\\
At the end of the strategy phase, you may spend 1 token from your strategy pool and give another player 3 of your trade goods. If you do, give 1 of your strategy cards to that player and take 1 of his strategy cards.
}

%The Empyrean

\newcommand{\aetherstream}{
\name{Aetherstream (BB)}{blue}\\
After you or one of your neighbors activate a system that is adjacent to an anomaly, you may apply +1 to the move value of all ships during that tactical action.
}

\newcommand{\voidwatch}{
\name{Voidwatch (G)}{green}\\
After a player moves ships into a system that contains 1 or more of your units, they must give you 1 promissory note from their hand, if able. 
}

%The Federation of Sol

\newcommand{\opsI}{
\name{Spec Ops Infantry I}\\
Cost 1(2) | Combat 7
}

\newcommand{\advancedCarrierI}{
\name{Advanced Carrier I}\\
Cost 3 | Combat 9 | Move 1 | Capacity 6
}

\newcommand{\opsII}{
\name{Spec Ops Infantry II (GG)}\\
Cost 1(2) | Combat 6\\
After this unit is destroyed, roll 1 die. If the result
is 5 or greater, place the unit on this card. At the
start of your next turn, place each unit that is on
this card on a planet you control in your home
system.
}

\newcommand{\advancedCarrierII}{
\name{Advanced Carrier II (BB)}\\
Cost 3 | Combat 9 | Move 2 | Capacity 8\\
\emph{Sustain Damage}
}

%The Ghosts of Creuss

\newcommand{\wormholeGenerator}{
\name{Wormhole Generator (BB)}{blue}\\
\emph{Action:}
Exhaust this card to place or move a Creuss wormhole token into either a system that contains a planet you control or a non-home system that does not contain another player's ships.
}

\newcommand{\splicer}{
\name{Dimensional Splicer (R)}{red}\\
At the start of a space combat in a system that
contains a wormhole and 1 or more of your ships,
you may produce 1 hit and assign it to 1 of your
opponent’s ships.
}

%The L1Z1X Mindnet

\newcommand{\superDreadsI}{
\name{Super Dreadnought I}\\
Cost 4 | Combat 5 | Move 1 | Capacity 2 \\
\emph{Sustain Damage}\\
\emph{Bombard} 5
}

\newcommand{\superDreadsII}{
\name{Super Dreadnought II (BBY)}\\
Cost 4 | Combat 4 | Move 2 | Capacity 2 \\
\emph{Sustain Damage}\\
\emph{Bombard} 4 \\
This unit cannot be destroyed by \emph{Direct Hit}.
}

\newcommand{\inheritence}{
\name{Inheritance Systems (YY)}{yellow}\\
You may exhaust this card and spend 2 resources
when you research a technology; ignore all of that
technology’s prerequisites.
}

%The Mahact Gene-Sorcerers

\newcommand{\legionnaireI}{
\name{Crimson Legionnaire Infantry I}\\
Cost 1(2) | Combat 8\\
After this unit is destroyed, gain 1 commodity or convert 1 of your commodities to a trade good.
}

\newcommand{\legionnaireII}{
\name{Crimson Legionnaire Infantry II (GG)}\\
Cost 1(2) | Combat 7\\
After this unit is destroyed, gain 1 commodity or convert 1 of your commodities to a trade good. Then, place the unit on this card. At the start of your next turn, place each unit that is on this card on a planet you control in your home system.
}

\newcommand{\genetic}{
\name{Genetic Recombination (G)}{green}\\
You may exhaust this card before a player casts votes; that player must cast at least 1 vote for an outcome of your choice or remove 1 token from their fleet pool and return it to their reinforcements.
}

%The Mentak Coalition

\newcommand{\salvageOperations}{
\name{Salvage Operations (YY)}{yellow}\\
After you win or lose a space combat,
gain 1 trade good;\\
If you won the combat, you may also produce
1 ship in that system of any ship type that was
destroyed during the combat.
}

\newcommand{\mirrorComputing}{
\name{Mirror Computing (YYY)}{yellow}\\
When you spend trade goods, each trade good is worth 2 resources or influence instead of 1.
}

%The Naalu Collective

\newcommand{\crystalFighterI}{
\name{Hybrid Crystal Fighter I}\\
Cost 1(2) | Combat 8
}

\newcommand{\crystalFighterII}{
\name{Hybrid Crystal Fighter II (GB)}\\
Cost 1(2) | Combat 7 | Move 2\\
This unit may move without being transported.
Each fighter in excess of your ships’ capacity
counts as 1/2 of a ship against your fleet pool.
}

\newcommand{\neuroglaive}{
\name{Neuroglaive (GGG)}{green}\\
After another player activates a system that
contains 1 or more of your ships, that player
removes 1 token from his fleet pool and returns it
to his reinforcements.
}

%The Naaz-Rokha Alliance

\newcommand{\supercharge}{
\name{Supercharge (R)}{red}\\
At the start of a combat round, you may exhaust this card to apply +1 to the result of each unit's combat rolls during this combat round. 
}

\newcommand{\arcologies}{
\name{Pre-Fab Arcologies (GGG)}{green}\\
After you explore a planet, ready that planet.
}

%The Nekro Virus

\newcommand{\valefar}{
\name{Valefar Assimilator X \& Y}\\
When you gain another player’s technology using
1 of your faction abilities, you may place the X/Y
assimilator token on a faction technology owned
by that player instead.\\
While that token is on a technology, this card
gains that technology’s text. You cannot place an
assimilator token on technology that already has
an assimilator token.
}

%The Nomad

\newcommand{\memoriaII}{
\name{Memoria II (GBY)}\\
Cost 8 | Combat 5x2 | Move 2 | Capacity 6 \\
\emph{Sustain Damage}\\
\emph{Anti-Fighter Barrage} 5x3\\
You may treat this unit as if it is adjacent to systems that contain 1 or more of your mechs.
}

\newcommand{\commandSuite}{
\name{Temportal Command Suite (Y)}{yellow}\\
After any player's agent becomes exhausted, you may exhaust this card to ready that agent. If you ready another player's agent you may perform a transaction with that player.
}
%Sardakk N'orr

\newcommand{\exoI}{
\name{Exotrireme Dreadnought I}\\
Cost 4 | Combat 5 | Move 1 | Capacity 1\\
\emph{Sustain Damage}\\
\emph{Bombard} 4x2
}

\newcommand{\exoII}{
\name{Exotrireme Dreadnought II (BBY)}\\
Cost 4 | Combat 5 | Move 2 | Capacity 1\\
\emph{Sustain Damage}\\
\emph{Bombard} 4x2\\
This unit cannot be destroyed by \emph{Direct Hit}.\\
After a round of space combat you may destroy
this unit to destroy up to 2 ships in this system.
}

\newcommand{\valkyrie}{
\name{Valkyrie Particle Weave (RR)}{red}\\
After making combat rolls during a round of
ground combat, if your opponent produced
1 or more hits, you produce 1 additional hit.
}

%The Titans of Ul

\newcommand{\helTitanI}{
\name{Hel Titan PDS I}\\
Combat 7\\
\emph{Planetary Shield}\\
\emph{Sustain Damage}\\
\emph{Space Cannon} 6\\
\emph{Production} 1\\
This unit is treated as both a structure and a ground force. It cannot be transported.
}

\newcommand{\saturnEngineI}{
\name{Saturn Engine Cruiser I}\\
Cost 2 | Combat 7 | Move 2 | Capacity 1
}

\newcommand{\helTitanII}{
\name{Hel Titan PDS II (YR)}\\
Combat 6\\
\emph{Planetary Shield}\\
\emph{Sustain Damage}\\
\emph{Space Cannon} 5\\
\emph{Production} 1\\
This unit is treated as both a structure and a ground force. It cannot be transported.\\
You may use this unit's \emph{Space Cannon} against ships that are adjacent to this unit's system.
}

\newcommand{\saturnEngineII}{
\name{Saturn Engine Cruiser II (GYR)}\\
Cost 2 | Combat 6 | Move 3 | Capacity 2\\
\emph{Sustain Damage}
}

%The Universities of Jol-Nar

\newcommand{\cylinder}{
\name{Spacial Conduit Cylinder (BB)}{blue}\\
You may exhaust this card after you activate
a system that contains 1 or more of your units;
that system is adjacent to all other systems
that contain 1 or more of your units during
this activation.
}

\newcommand{\eres}{
\name{E-Res Siphons (YY)}{yellow}\\
After another player activates a system
that contains 1 or more of your ships,
gain 4 trade goods.
}

%The Vuil'Raith Cabal

\newcommand{\dimensionalTearI}{
\name{Dimenional Tear Space Dock I}\\
\emph{Production} 5\\
This system is a gravity rift; your ships do not roll for this gravity rift. Place a dimensional tear token beneath this unit as a reminder.\\
Up to 6 fighters in this system do not count against your ships' capacity. 
}

\newcommand{\dimensionalTearII}{
\name{Dimenional Tear Space Dock II (YY)}\\
\emph{Production} 7\\
This system is a gravity rift; your ships do not roll for this gravity rift. Place a dimensional tear token beneath this unit as a reminder.\\
Up to 12 fighters in this system do not count against your ships' capacity. 
}

\newcommand{\vortex}{
\name{Vortex (R)}{red}\\
\emph{Action:} Exhaust this card to choose another player's non-structure unit in a system that is adjacent to 1 or more of your space docks. Capture 1 unit of that type from that player's reinforcements.
}

%The Winnu

\newcommand{\gateFolding}{
\name{Lazax Gate Folding (BB)}{blue}\\
If you do not control Mecatol Rex, treat its system
as if it contains both an alpha and beta wormhole.\\
\emph{Action:} If you control Mecatol Rex, exhaust this
card to place 1 infantry on Mecatol Rex.
}

\newcommand{\hegemonic}{
\name{Hegemonic Trade Policy (YY)}{yellow}\\
Exhaust this card when 1 or more of your units use \emph{Production}; swap the resource and influence values of 1 planet you control during that use of \emph{Production}.
}%ERRATAD

%The Xxcha Kingdom

\newcommand{\instinct}{
\name{Instinct Training (G)}{green}\\
You may exhaust this card and spend 1 token from
your strategy pool when another player plays an
action card; cancel that action card.
}

\newcommand{\nullification}{
\name{Nullification Field (YY)}{yellow}\\
After another player activates a system that
contains 1 or more of your ships, you may exhaust
this card and spend 1 token from your strategy
pool; immediately end that player’s turn.
}

%The Yin Brotherhood

\newcommand{\impulseCore}{
\name{Impulse Core (YY)}{yellow}\\
At the start of a space combat, you may destroy
1 of your cruisers or destroyers in the active
system to produce 1 hit against your opponent’s
ships; that hit must be assigned by your opponent
to 1 of his non-fighter ships if able.
}

\newcommand{\spinner}{
\name{Yin Spinner (GG)}{green}\\
After you produce units, place up to 2 infantry from your reinforcements on any planet you control or in any space area that contains 1 or more of your ships.
}

%The Yssaril Tribes

\newcommand{\transparasteel}{
\name{Transparasteel Plating (G)}{green}\\
During your turn of the action phase, players that
have passed cannot play action cards.
}

\newcommand{\mageon}{
\name{Mageon Implants (GGG)}{green}\\
\emph{Action:}
Exhaust this card to look at another player’s hand
of action cards. Choose 1 of those cards and add
it to your hand.
}