%Warfare - Red

\newcommand{\plasma}{
\name{Plasma Scoring}{red} \techlevel{red}{0}\\
When 1 or more of your units use \emph{Bombardment} or \emph{Space Cannon}, 1 of those rolls may roll 1 additional die.
}

\newcommand{\development}{
\name{AI Development Algorithm}{red} \techlevel{red}{0}\\
UNKNOWN.
} %TODO add content

\newcommand{\assembly}{
\name{Self Assembly Routines}{red} \techlevel{red}{1}\\
After 1 or more of your units use \emph{Production}, you may exhaust this card to place 1 mech from your reinforcements on a planet you control in that system.\\
After 1 of your mechs is destroyed, gain 1 trade good.
}

\newcommand{\magen}{
\name{Magen Defense Grid}{red} \techlevel{red}{1}\\
At the start of ground combat on a planet the contains 1 or more of your structures, you may produce 1 hit and assign it to 1 of your opponent's ground forces.
}

\newcommand{\duranium}{
\name{Duranium Armor}{red} \techlevel{red}{2}\\
During each combat round, after you assign hits to your units, repair 1 of your damaged units that did not use Sustain Damage during this combat round.
}

\newcommand{\assault}{
\name{Assault Cannon}{red} \techlevel{red}{3}\\
At the start of a space combat in a system that contains 3 or more of your non-fighter ships, your opponent must destroy 1 of his non-fighter ships.
}

%Cybernetic - Yellow

\newcommand{\sarween}{
\name{Sarween Tools}{yellow} \techlevel{yellow}{0}\\
When 1 or more of your units use \emph{Production}, reduce the combined cost of the produced units by 1.
}

\newcommand{\scanlink}{
\name{Scanlink Drone Network}{yellow} \techlevel{yellow}{0}\\
When you activate a system, you may explore 1 planet in that system that contains 1 or more of your units.
}

\newcommand{\graviton}{
\name{Graviton Laer System}{yellow} \techlevel{yellow}{1}\\
You may exhaust this card before 1 or more of your units uses \emph{Space Cannon}; hits produced by those units must be assigned to non-fighter ships if able.
}

\newcommand{\predictive}{
\name{Predictive Intelligence}{yellow} \techlevel{yellow}{1}\\
At the end of your turn, you may exhaust this card to redistribute your command tokens.\\
When you cast votes during the agenda phase, you may cast 3 additional votes. If you do, and the outcome you voted for is not resolved, exhaust this card.
}

\newcommand{\transit}{
\name{Transit Diodes}{yellow} \techlevel{yellow}{2}\\
You may exhaust this card at the start of your turn during the action phase; remove up to 4 of your ground forces from the game board and place them on 1 or more planets you control.
}

\newcommand{\integrated}{
\name{Integrated Economy}{yellow} \techlevel{yellow}{3}\\
After you gain control of a planet, you may produce any number of units on that planet that have a combined cost equal to or less than that planet’s resource value.
}

%Biotic - Green

\newcommand{\neural}{
\name{Neural Motivator}{green} \techlevel{green}{0}\\
During the status phase, draw 2 action cards instead of 1.
}

\newcommand{\psycho}{
\name{Psychoarchaeology}{green} \techlevel{green}{0}\\
UNKNOWN.
} %TODO add content

\newcommand{\deaxive}{
\name{Deaxive Animators}{green} \techlevel{green}{1}\\
After you win a ground combat, you may place 1 infantry from your reinforcements on that planet.
}

\newcommand{\biostims}{
\name{Bio-Stims}{green} \techlevel{green}{1}\\
UNKNOWN.
} %TODO add content

\newcommand{\hyper}{
\name{Hyper Metabolism}{green} \techlevel{green}{2}\\
During the status phase, gain 3 command tokens instead of 2.
}

\newcommand{\bacterial}{
\name{X-89 Bacterial Weapon}{green} \techlevel{green}{3}\\
After 1 or more of your units use \emph{Bombardment} against a planet, if at least 1 of your opponent's infantry was destroyed, you may destroy all of your opponent's infantry on that planet.
}

%Propulsion - Blue

\newcommand{\antimass}{
\name{Antimass Deflectors}{blue} \techlevel{blue}{0}
Your ships can move into and through asteroid fields.\\
When other players’ units use \emph{Space Cannon} against your units, apply -1 to the result of each die roll.
}

\newcommand{\tap}{
\name{Dark Energy Tap}{blue} \techlevel{blue}{0}
After you perform a tactical action in a system that contains a frontier token, if you have 1 or more ships in that system explore that token.\\
Your ships can retreat into adjacent systems that do not contain other players' units even if you do not have unit or control planets in that system.
}

\newcommand{\gravdrive}{
\name{Gravity Drive}{blue} \techlevel{blue}{1}
After you activate a system, apply +1 to the move value of 1 of your ships during this tactical action.
}

\newcommand{\sling}{
\name{Sling Relay}{blue} \techlevel{blue}{1}
\emph{Action:}
Exhaust this card to produce one ship in any system that contains one of your space docks.
}

\newcommand{\logistics}{
\name{Fleet Logistics}{blue} \techlevel{blue}{2}
During each of your turns of the action phase, you may perform 2 actions instead of 1.
}

\newcommand{\lightwave}{
\name{Light/Wave Deflector}{blue} \techlevel{blue}{3}
Your ships can move through systems that contain other player’s ships.
}