{\handel \Huge The Arborec} \hfill {\Large Difficulty: \hard} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Mitosis}\\
Your space docks cannot produce infantry. At the start of the status phase, place 1 infantry from your reinforcements on any planet you control.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 carrier
\item 1 cruiser
\item 2 fighters
\item 4 infantry
\item 1 space dock
\item 1 PDS
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 3

\vspace{2pt}
\stress{Home System}: Nestphar (3/2)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \magen
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Duha Menaimon}\\
Cost 8 | Combat 7x2 | Move 1 | Capacity 5 \\
\emph{Sustain Damage}\\
After you activate this system you may produce up to 5 units in this system.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Name} %TODO add name
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
\emph{Production} 2\\
\emph{Planetary Shield}\\
When you use your \emph{Mitosis}
faction ability you may replace 1 of your infantry with a mech from your reinforcements instead. 
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Special Units}

\begin{itemize}
\item \letaniI
\end{itemize}

%\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \letaniII
\item \bioplasmosis
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Letani Ospha}\\
\emph{Action:}
Exhaust this card and choose a player's non-fighter ship. That player may replace that ship with one from their reinforcements that costs up to two more than the replaced ship.
\item \name{Commander - Drzuga Rophal} \textcolor{gray}{(\emph{Unlock:} Unknown)} %TODO fill in
After another player activates a system that contains 1 or more of your units that have \emph{Production},
you may produce 1 unit in that system.
\item \name{Hero - Ultrasonic Emitter / Overgrowth} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{Action:} Produce any number of units in any number of systems that contain 1 or more of your ground forces. Then purge this card.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Stymie}\\
\emph{After another player moves ships into a system that contains 1 or more of your units:}\\
You may place 1 command token from that player's reinforcements in any non-home system.
\\
Then return this card to the Arborec player.
\end{itemize}

\end{multicols}

