{\handel \Huge The Argent Flight} \hfill {\Large Difficulty: Unkown} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Zeal}\\
You always vote first during the agenda phase.\\
When you cast at least 1 vote, cast 1 additional vote for each player in the game including you.
\item \name{Raid Formation}\\
When 1 or more of your units uses \emph{Anti-Fighter Barrage}, for each hit produced in excess of your opponent's fighters, choose 1 of your opponent's ships that has \emph{Sustain Damage} to become damaged.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 carrier
\item 2 destroyers
\item 2 fighters
\item 5 infantry
\item 1 space dock
\item 1 PDS
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 3

\vspace{2pt}
\stress{Home System}: Avar (1/1); Valk (2/0); Yur (0/2)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

Choose 2 of the following.

\begin{itemize}
\item \neural
\item \sarween
\item \plasma
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Quetzecoatl}\\
Cost 8 | Combat 7x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
Other players cannot use \emph{Space Cannon} against your ships in this system.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Aerie Sentinel}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
This unit does not count against capacity if it is being transported or if it is in a space area with 1 or more of your ships that have capacity values.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Special Units}

\begin{itemize}
\item \strikeWingI
\end{itemize}

%\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \strikeWingII
\item \hololattice
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Trillossa Aun Mirik}\\
\emph{Action:}
\emph{When a player produces ground forces in a system:}
\\
You may exhaust this card; that player may place those units on any planets they control in that system and any adjacent systems. 
\item \name{Commander - Trrakan Aun Zulok} \textcolor{gray}{(\emph{Unlock:} Have 6 units that have \emph{Anti-Fighter Barrage}, \emph{Space Cannon} or \emph{Bombardment} on the game board.)}\\
\emph{When 1 or more of your units make a roll for a unit ability:}
\\
You may choose 1 of those units to roll 1 additional die. 
\item \name{Hero - Mirik Aun Sissiri / Helix Protocol} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{Action:} Move any number of your ships from any systems to any number of other systems that contain 1 of your command tokens and no other players' ships.
\\
Then, purge this card. 
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Strike Wing Ambuscade}\\
\emph{When 1 or more of your units make a roll for a unit ability:}\\
Choose 1 of those units to roll 1 additional die.
\\
Then return this card to the Argent player.
\end{itemize}

\end{multicols}



