{\handel \Huge The Barony of Letnev} \hfill {\Large Difficulty: \easy} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Munitions Reserves}\\
At the start of each round of space combat, you may spend 2 trade goods; you may reroll any number of your dice during that combat round.
\item \name{Armada}\\
The maximum number of non-fighter ships you can have in each system is equal to 2 more than the number of tokens in your fleet pool.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 dreadnought
\item 1 carrier
\item 1 destroyer
\item 1 fighter
\item 3 infantry
\item 1 space dock
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 2

\vspace{2pt}
\stress{Home System}: Arc Prime (4/0); Wren Terra (2/1)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \antimass
\item \plasma
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Arc Secundus}\\
Cost 8 | Combat 5x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
\emph{Bombardment} 5x3\\
Other players' units in this system lose \emph{Planetary Shield}. At the start of each space combat round, repair this ship.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Dunlain Reaper}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
\emph{Deploy:} At the start of a round of ground combat, you may spend 2 resources to replace 1 of your infantry in that combat with 1 mech.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \disruptors
\item \NES
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Viscount Unlenn}\\
At the start of a space combat round exhaust this card to chose 1 ship in the active system, that ship rolls 1 additional die in this combat round.
\item \name{Commander - Unknown.} \textcolor{gray}{(\emph{Unlock:} Have 5 non-fighter ships in 1 system.)}\\
Unknown.
\item \name{Hero - Unknown.} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
Unknown.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{War Funding}\\
\emph{After you and your opponent roll dice during space combat:}\\
You may reroll all of your opponent's dice.\\
You may reroll any number of your dice.\\
Then, return this card to the Letnev player.
\end{itemize}

\end{multicols}



