{\handel\Huge The Vuli'raith Cabal} \hfill {\Large Difficulty: Unknown} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Devour}\\
Capture your opponents' non-structure units that are destroyed during combat.
\item \name{Amalgamation} When you produce a unit, you may return 1 captured unit of that type to produce that unit without spending resources.
\item \name{Riftmeld} When you research a unit upgrade technology, you may return 1 captured unit of that type to ignore all of that technology's prerequisites.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 dreadnought
\item 1 carrier
\item 1 cruiser
\item 3 fighters
\item 3 infantry
\item 1 space dock
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 2

\vspace{2pt}
\stress{Home System}: Acheron (4/0)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \assembly
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{The Terror Between}\\
Cost 8 | Combat 5x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
\emph{Bombardment} 5\\
Capture all other non-structure units that are destroyed in this unit's system, including your own.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Reanimator}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
When your infantry on this planet are destroyed, place them on your faction sheet; those units are captured.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Special Units}

\begin{itemize}
\item \dimensionalTearI
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}
\stress{Faction Technologies}

\begin{itemize}
\item \dimensionalTearII
\item \vortex
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - The Stillness of Stars}\\
\emph{After another player replenishes commodities:}
\\
You may exhaust this card to convert their commodities to trade goods and capture 1 unit from their reinforcements that has a cost equal to or lower than their commodity value.
\item \name{Commander - That Which Molds Flesh} \textcolor{gray}{(\emph{Unlock:} Have units in 3 Gravity Rifts)}\\
\emph{When you produce fighter or infantry units:}
\\
Up to 2 of those units do not count against your \emph{Production} limit. 
\item \name{Hero - It Feeds on Carrion / Dimensional Anchor} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{Action:} Each other player rolls a die for each of his non-fighter ships that are in or adjacent to a system that contains a dimensional tear; on a 1-3, capture that unit. If this causes a player's ground forces or fighters to be removed, also capture those units.\\
Then, purge this card.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Crucible}\\
\emph{After you activate a system:}

Your ships do not roll for gravity rifts during this movement; apply an additional +1 to the move values of your ships that would move out of or through a gravity rift instead.

Then, return this card to the Vuil'raith player. 
\end{itemize}

\end{multicols}



