{\handel\Huge The Empyrean} \hfill {\Large Difficulty: Unknown} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Voidborn}\\
Nebluae do not affect your ships' movement.
\item \name{Aetherpassage}\\
After a player activates a system, you may allow that player to move their ships through systems that contain your ships.
\item \name{Dark Whispers}\\
During setup, take the additional Empyrean faction promissory note: you have 2 faction promissory notes.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 2 carrier
\item 1 destroyer
\item 2 fighters
\item 4 infantry
\item 1 space dock
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 4

\vspace{2pt}
\stress{Home System}: The Dark (3/4); \emph{Nebula}

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \tap
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Dynamo}\\
Cost 8 | Combat 5x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
After any player's unit in this system or an adjacent system uses \emph{Sustain Damage}, you may spend 2 influence to repair that unit.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Watcher}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
You may remove this unit from a system that contains or is adjacent to another player's units to cancel an action card played by that player.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \aetherstream
\item \voidwatch
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Acamar}\\
\emph{After a player moves ships into a system that does not contain any planets:}
\\
You may exhaust this card; that player gains 1 command token 
\item \name{Commander - Xuange} \textcolor{gray}{(\emph{Unlock:} Be neighbors with all other players)}\\
\emph{After another player moves ships into a system that contains 1 of your command tokens:}
\\
You may return that token to your reinforcements.
\item \name{Hero - Conservator Procyon / Multiverse Shift} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{Action:} Place 1 frontier token in each system that does not contain any planets and does not already have a frontier token. Then, explore each frontier token that is in a system that contains 1 or more of your ships. Then, purge this card.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Notes}

\begin{itemize}
\item \name{Blood Pact}\\
\emph{Action:} Place this card faceup in your play area.\\
When you and the Empyrean player cast votes for the same outcome, cast 4 additional votes for that outcome. If you activate a system containing 1 or more of the Empyrean player's units, return this card to the Empyrean player.
\item \name{Dark Pact}
\emph{Action:} Place this card faceup in your play area.\\
When you give a number of commodities to the Empyrean player equal to your maximum commodity value, you each gain one trade good. If you activate a system containing 1 or more of the Empyrean player's units, return this card to the Empyrean player.
\end{itemize}

\end{multicols}



