\newpage
{\handel\Huge The Emirates of Hacan} \hfill {\Large Difficulty: \easy} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Masters of Trade}\\
You do not have to spend a command token to resolve the secondary ability of the ``Trade" strategy card.
\item \name{Guild Ships}\\
You can negotiate transactions with players who are not your neighbour.
\item \name{Arbiters}\\
When you are negotiating a transaction, action cards can be exchanged as part of that transaction.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 2 carriers
\item 1 cruiser
\item 2 fighters
\item 4 infantry
\item 1 space dock
\color{white}
\item 1 PDS
\color{black}
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 6

\vspace{2pt}
\stress{Home System}: Arretze (2/0); Hercant (1/1); Kamdorn (0/1)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \antimass
\item \sarween
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Wrath of Kenara}\\
Cost 8 | Combat 7x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
After you roll a die during a space combat in this system, you may spend 1 trade good to apply +1 to the result.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Pride of Kenara}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
This planet’s planet card may be traded as part of a transaction, if you do, move all of your units from this planet to another planet you control.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \biomes
\item \datahub
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Carth of Golden Sands}\\
\emph{Action:}
\emph{During the action phase:}\\
You may exhaust this card to gain 2 commodities or replenish another player's commodities
\item \name{Commander - Unknown} \textcolor{gray}{(\emph{Unlock:} Unknown)}
Unknown.
\item \name{Hero - Harrugh Gefhara} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{When 1 or more of your units use \emph{Production}:}, you may reduce the cost of each of your units to 0 during the use of \emph{Production}. If you do, purge this card. 
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Trade Convoys}\\
\emph{Action:} Place this card face up in your play area.\\
While this card is in your play area, you may negotiate transactions with players who are not your neighbour.\\
If you activate a system that contains 1 or more of the Hacan player's units, return this card to the Hacan player.
\end{itemize}

\end{multicols}



