{\handel\Huge The Universities of Jol-Nar} \hfill {\Large Difficulty: \easy} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Fragile}\\
Apply -1 to the result of each of your unit's combat rolls.
\item \name{Brilliant}\\
When you spend a command token to resolve the secondary ability of the ``Technology" strategy card, you may resolve the primary ability instead.
\item \name{Analytical}\\
When you research a technology that is not a unit upgrade technology, you may ignore 1 prerequisite.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 dreadnought
\item 2 carriers
\item 1 fighter
\item 2 infantry
\item 1 space dock
\item 2 PDS
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 4

\vspace{2pt}
\stress{Home System}: Jol (1/2), Nar (2/3)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \neural
\item \antimass
\item \sarween
\item \plasma
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{J.N.S. Hylarim}\\
Cost 8 | Combat 6x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
When making a combat roll for this ship, each result of 9 or 10, before applying modifiers, produces 2 additional hits.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech} %TODO add

\begin{itemize}
\item \name{UNKNOWN}
\\
UNKNOWN.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \cylinder
\item \eres
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - UNKNOWN}\\
UNKNOWN.
\item \name{Commander - Ta Zern} \textcolor{gray}{(\emph{Unlock:} UNKNOWN)}
After you roll dice for a unit ability: You may reroll any of those dice.
\item \name{Hero - Rin / The Master's Legacy} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{Action:} For each non-unit upgrade technology you own, you may replace that technology with any technology of the same color from the deck. Then, purge this card. 
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Research Agreement}\\
\emph{After the Jol-Nar player researches a technology that is not a faction technology:}\\
Gain that technology.\\
Then, return this card to the Jol-Nar player.
\end{itemize}

\end{multicols}



