{\handel\Huge The Council Keleres} \hfill {\Large Difficulty: \medium} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{The Tribuni}\\
During setup, choose an unplayed faction from among the {Mentak}, the {Xxcha} and {The Argent Flight}; take that faction's home system, command tokens and control markers. Additionally, take the Keleres Hero that corresponds to that faction.
\item \name{Council Patronage}\\
Replenish your commodities at the start of the strategy phase, then gain 1 {trade good}.
\item \name{Law's Order}\\
You may spend 1 influence at the start of your turn to treat all laws as blank until the end of your turn.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 2 carriers
\item 1 cruiser
\item 2 fighters
\item 2 infantry
\item 1 space dock
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 3

\vspace{2pt}
\stress{Home System}: One of the following:
\begin{itemize}
\item \name{The Mentak Coalition:} Moll Primus (4/1)
\item \name{The Xxcha Kingdom:} Archon Ren (2/3); Archon Tau (1/1)
\item \name{The Argent Flight:} Avar (1/1); Valk (2/0); Yur (0/2)
\end{itemize}

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \name{Choose any 2 non-faction technologies owned by other players.}
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Artemiris}\\
Cost 8 | Combat 7x2 | Move 1 | Capacity 6 \\
\emph{Sustain Damage}\\
Other players must spend 2 influence to activate the system that contains this ship.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Omniopiares}
\\
Cost 2 | Combat 6
\\
\emph{Sustain Damage}
\\
Other players must spend 1 influence to commit ground forces to the planet that contains this unit.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \iihq
\item \asn
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Xander Alexin Victori III}\\
\emph{At any time:} You may exhaust this card to allow any player to spend commodities as if they were trade goods.
\item \name{Commander - Suffi An} \textcolor{gray}{(\emph{Unlock:} Spend 1 trade good after you play an action card that has a component action.)} \\
\emph{After you perform a component action:}\\ You may perform an additional action.
\item \name{Hero - Depends on the faction chosen as Tribuni:}

\begin{itemize}
\item \name{Mentak Coalition Hero - Harka Leeds / Erwan's Covenant}\textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{Action:} Reveal cards for the action deck until you reveal 3 action cards that have component actions. Draw those cards and shuffle the rest back into the action card deck.\\
Then, purge this card.

\item \name{Xxcha Kingdom Hero - Odlynn Myrr / Operation Archon}\textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{After an agenda is revealed:}\\
You may case up to 6 additional votes on this agenda. Predict aloud an outcome of this agenda. For each player that votes for another outcome, gain 1 trade good and 1 command token.\\
Then, purge this card.

\item \name{Argent Flight Hero - Kuuasi Aun Jalatai / Overwing Zeta} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{At the start of a round of space combat in a system that contains a planet you control:}\\ Place your flagship and up to a total of 2 cruisers and/or destroyers from your reinforcements in the active system.\\Then, purge this card.
\end{itemize}
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Keleres Rider}:\\
\emph{After an agenda is revealed:}\\
You cannot vote on this agenda. Predict aloud an outcome of this agenda. If your prediction is correct, draw 1 action card and gain 2 trade goods.\\
Then, return this card to the Keleres player.
\end{itemize}

\end{multicols}



