{\handel\Huge The L1Z1X Mindnet} \hfill {\Large Difficulty: \easy} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Assimilate}\\
When you gain control of a planet, replace each PDS and space dock that is on that planet with a matching unit from your reinforcements.
\item \name{Harrow}\\
At the end of each round of ground combat, your ships in the active system may use their bombardment abilities against your opponent's ground forces on the planet.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 dreadnought
\item 1 carrier
\item 3 fighters
\item 5 infantry
\item 1 space dock
\item 1 PDS
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 2

\vspace{2pt}
\stress{Home System}: [0.0.0] (5/0)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \neural
\item \plasma
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{[0.0.1]}\\
Cost 8 | Combat 5x2 | Move 1 | Capacity 5 \\
\emph{Sustain Damage}\\
During a space combat, hits produced by this ship and by your dreadnoughts in this system must be assigned to non-fighter ships if able.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Annihilator}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
\emph{Bombardment 8}\\
While not participating in ground combat, this unit can use its \emph{Bombardment} ability on planets in its system as if it were a ship.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Special Units}

\begin{itemize}
\item \superDreadsI
\end{itemize}

%\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \superDreadsII
\item \inheritence
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - I48S}\\
\emph{After a player activates a system:}
\\
You may exhaust this card to allow that player to replace 1 of their infantry in the active system with 1 mech from their reinforcements.
\item \name{Commander - 2RAM} \textcolor{gray}{(\emph{Unlock:} Have 4 dreadnoughts on the board)}\\
Units that have \emph{Planetary Shield} do not prevent you from using \emph{Bombardment}.
\item \name{Hero - The Helmsman / Dark Space Navigation} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{ACTION:} Choose 1 system that does not contain other players' ships; you may move your flagship and any number of your dreadnoughts from other systems into the chosen system.

Then, purge this card. 
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Cybernetic Enhancements}\\
\emph{When you gain command tokens during the status phase:}\\
Gain 1 additional command token.\\
Then, return this card to the L1Z1X player.
\end{itemize}

\end{multicols}



