{\handel\Huge The Mahact Gene-Sorcerers} \hfill {\Large Difficulty: Unknown} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Edict}\\
When you win a combat, place 1 command token from your opponent's reinforcements in your fleet pool if it does not already contain 1 of that player's tokens; other player's tokens in your fleet pool increase your fleet limit but cannot be redistributed.
\item \name{Imperia}\\
While another player's command token is in your fleet pool, you can use the ability of that player's commander, if it is unlocked.
\item \name{Hubris}\\
During setup, purge your ``Alliance" promissory note Other players cannot give you their ``Alliance" promissory notes.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 dreadnought
\item 1 carrier
\item 1 cruiser
\item 2 fighters
\item 3 infantry
\item 1 space dock
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 3

\vspace{2pt}
\stress{Home System}: Ixth (3/5)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \biostims
\item \predictive
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Arvicon Rex}\\
Cost 8 | Combat 5x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
During combat against an opponent whose command token is not in your fleet pool, apply +2 to the results of this unit's combat rolls.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Starlancer}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
After a player whose command token is in your fleet pool activates this system, you may spend their token from your fleet pool to end their turn; they gain that token.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Special Units}

\begin{itemize}
\item \legionnaireI
\end{itemize}

%\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \legionnaireII
\item \genetic
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Jae Mir Kan}\\
\emph{When you would spend a command token during the secondary ability of a strategic action:}
\\
You may exhaust this card to remove 1 of the active player's command tokens from the board and use it instead.
\item \name{Commander - Il Na Viroset} \textcolor{gray}{(\emph{Unlock:} Have 2 other factions' command tokens in your fleet pool.)}\\
During your tactical actions, you can activate systems that contain your command tokens. If you do, return both command tokens to your reinforcements and end your turn. 
\item \name{Hero - Airo Shir Aur / Benediction} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{Action:} Move all units in the space area of any system to an adjacent system that contains a different player's ships. Space Combat is resolved in that system; neither player can retreat or resolve abilities that would move their ships. Then, purge this card.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Scepter of Dominion}\\
\emph{At the start of the strategy phase: }

Choose 1 non-home system that contains your units; each other player who has a token on the Mahact player's command sheet places a token from their reinforcements in that system

Then, return this card to the Mahact player. 
\end{itemize}

\end{multicols}



