\newpage
{\handel\Huge The Mentak Coalition} \hfill {\Large Difficulty: \medium} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Ambush}\\
At the start of a space combat, you may roll 1 die for each of up to 2 of your cruisers or destroyers in the system. For each result equal to or greater than the ship's combat value, produce 1 hit; your opponent must assign it to 1 of his ships.
\item \name{Pillage}\\
After 1 of your neighbours gains trade goods or resolves a transaction, if he has 3 or more trade goods, you may take 1 of his trade goods or commodities.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 carrier
\item 2 cruisers
\item 3 fighters
\item 4 infantry
\item 1 space dock
\item 1 PDS
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 2

\vspace{2pt}
\stress{Home System}: Moll Primus (4/1)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \sarween
\item \plasma
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Fourth Moon}\\
Cost 8 | Combat 7x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
Other players' ships in this systems cannot use \emph{Sustain Damage}.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Unknown} %TODO add
\\
Unknown.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \salvageOperations
\item \mirrorComputing
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders} %TODO add

\begin{itemize}
\item \name{Agent - Unknown}\\
Unknown.
\item \name{Commander - Unknown} \textcolor{gray}{(\emph{Unlock}: Unknown)} %TODO fill in
\emph{After you win a space combat:}\\
You may force your opponent to give you 1 promissory note from their hand.
\item \name{Hero - Ipsw??? / Sleeper Cell} \textcolor{gray}{(\emph{Unlock}: Have 3 scored objectives)}\\
\emph{At the start of space combat that you are participating in:}\\
You may purge this card; if you do, for each other player’s ship that is destroyed during this combat, place 1 ship of that type from your reinforcements in the active system.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Promise of Protection}\\
\emph{Action:} Place this card face-up in your play area.\\
While this card is in your play area, the Mentak player cannot use his \emph{Pillage} faction ability againt you.\\
If you activate a system that contains 1 or more of the Mentak player's units, return this card to the Mentak player.
\end{itemize}

\end{multicols}



