{\handel\Huge The Embers of Muaat} \hfill {\Large Difficulty: \hard} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Star Forge}\\
\emph{Action:}
Spend 1 token from your strategy pool to place either 2 fighters or 1 destroyer from your reinforcements in a system that contains 1 or more of your war suns.
\item \name{Gashlai Physiology}\\
Your ships can move through supernovas.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 war sun
\item 2 fighters
\item 4 infantry
\item 1 space dock
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 4

\vspace{2pt}
\stress{Home System}: Muuat (4/1)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \plasma
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{The Inferno}\\
Cost 8 | Combat 5x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
\emph{Action:} Spend 1 token from your strategy pool to place 1 cruiser in this unit's system.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Ember Colossus}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
When you use your \emph{Star Forge} faction ability in this system or an adjacent system, you may place 1 infantry from your reinforcements with this unit.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Special Units}

\begin{itemize}
\item \prototypeI
\end{itemize}

%\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \prototypeII
\item \magmus
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Umbat}\\
\emph{Action:} Exhaust this card to choose a player; that player may produce up to 2 units that each have a cost of 4 or less in a system that contains one of their war suns or their flagship.
\item \name{Commander - Magmus} \textcolor{gray}{(\emph{Unlock}: Produce a War Sun)}\\
After you spend a token from your strategy pool: You may gain 1 trade good.
\item \name{Hero - Adjudicator Ba'al / Nova Seed} \textcolor{gray}{(\emph{Unlock}: Have 3 scored objectives)}\\
\emph{After you move a war sun into a non-home system other than Mecatol Rex:}\\
You may destroy all other players' units in that system and replace that system tile with the Muaat supernova tile. If you do, purge this card and each planet card that corresponds to the replaced system tile
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Fires of the Gashlai}\\
\emph{Action:}
Remove 1 token from the Muaat player's fleet pool and return it to his reinforcements. Then, gain your war sun unit upgrade technology card.\\
Then, return this card to the Muaat player.
\end{itemize}

\end{multicols}



