{\handel\Huge The Naalu Collective} \hfill {\Large Difficulty: \medium} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Telepathic}\\
At the end of the strategy phase, place the Naalu ``0'' token on your strategy card; you are the first in initiative order.
\item \name{Foresight}\\
After another player moves ships into a system that contains 1 or more of your ships, you may place 1 token from your strategy pool in an adjacent system the does not contain another player's ships; move your ships from the active system into that system.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 carrier
\item 1 cruiser
\item 1 destroyer
\item 3 fighters
\item 4 infantry
\item 1 space dock
\item 1 PDS
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 3

\vspace{2pt}
\stress{Home System}: Druaa (3/1); Maaluuk (0/2)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \neural
\item \sarween
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship} %ERRATA'd

\begin{itemize}
\item \name{Matriarch}\\
Cost 8 | Combat 9x2 | Move 1 | Capacity 6 \\
\emph{Sustain Damage}\\
During an invasion in this system, you may commit fighters to planets as if they were ground forces. When combat ends, return those units to the space area.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Iconoclast}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
Other players cannot use \emph{Anti-Fighter Barrage} against your units in this system.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Special Units}

\begin{itemize}
\item \crystalFighterI
\end{itemize}

%\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \crystalFighterII
\item \neuroglaive
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Z'Eu}\\
\emph{Action:}
Exhaust this card and choose a player; that player may perform a tactical action in a non-home system without placing a command token; that system still counts as being activated.
\item \name{Commander - M’Aban} \textcolor{gray}{(\emph{Unlock:} Have ground forces in or adjacent to the Mecatol Rex system)}\\
\emph{At any time:}\\
You may look at your neighbors' hands of promissory notes and the top and bottom card of the agenda deck.
\item \name{Hero - The Oracle / C-Radium Geometry} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{At the end of the status phase:}

You may force each other player to give you 1 promissory note from their hand. If you do, purge this card.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Gift of Prescience}\\
\emph{At the end of the strategy phase:}\\
Place this card faceup in your play area and place the Naalu ``0" token on your strategy card; you are first in initiative order. The Naalu player cannot use his \emph{Telepathic} faction ability during this game round.\\
Return this card to the Naalu player at the end of the status phase.
\end{itemize}

\end{multicols}



