{\handel\Huge The Naaz-Rokha Alliance} \hfill {\Large Difficulty: Unknown} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Distant Suns}\\
When you explore a planet that contains 1 of your mechs, you may draw 1 additional card; choose 1 to resolve and discard the rest.
\item \name{Fabrication} \\
\emph{Action:} Either purge 2 of your relic fragments of the same type to gain 1 new relic or purge 1 of your relic fragments to gain 1 command token.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 2 carriers
\item 1 destroyer
\item 2 fighters
\item 1 mech
\item 3 infantry
\item 1 space dock
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 3

\vspace{2pt}
\stress{Home System}: Naazir (2/1); Rokha (1/2)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \psycho
\item \development
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Visz El Vir}\\
Cost 8 | Combat 9x2 | Move 1 | Capacity 4 \\
\emph{Sustain Damage}\\
Your mechs in this system roll 1 additional die during combat.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Eidolon} \textcolor{gray}{(mech side)}
\\
Cost 2 | Combat 6x2 \\
If this unit is in the space area of the active system at the start of a space combat, flip this card.
\item \name{Z-Grav Eidolon} \textcolor{gray}{(flipped card)}
\\
If this unit is in the space area of the active system, it is a ship. At the end of a space battle in the active system, flip this card.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \arcologies
\item \supercharge
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Garv and Gunn}\\
At the end of a player's turn, you may exhaust this card to allow the player to explore 1 of their planets.
\item \name{Commander - Dart and Tai} \textcolor{gray}{(\emph{Unlock:} Have mechs in 3 systems.)}\\
After you gain control of a planet that was controlled by another player, you may explore that planet
\item \name{Hero - Hesh and Prit} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{Action:} Gain 1 relic and perform the secondary ability of up to 2 readied or unchosen strategy cards; during this action, spend command tokens from your reinforcements instead of your strategy pool. 
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Black Market Forgery}\\
\emph{Action:} Purge 2 of your relic fragments of the same type to gain one relic. Then, return this card to the Naaz-Rokha player.
\end{itemize}

\end{multicols}



