\newpage
{\handel\Huge The Nekro Virus} \hfill {\Large Difficulty: \hard} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Galactic Threat}\\
You cannot vote on agendas. Once per agenda phase, after an agenda is revealed, you may predict aloud the outcome of that agenda. If your prediction is correct, gain 1 technology that is owned by a player who voted how you predicted.
\item \name{Technological Singularity}\\
Once per combat, after 1 of your opponent's units is destroyed, you may gain 1 technology that is owned by that player.
\item \name{Propagation}\\
You cannot research technology. When you would research a technology, gain 3 command tokens instead.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 dreadnought
\item 1 carrier
\item 1 cruier
\item 2 fighters
\item 2 infantry
\item 1 space dock
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 3

\vspace{2pt}
\stress{Home System}: Mordai II (4/0)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \deaxive
\item \name{Valefar Assimilator X}
\item \name{Valefar Assimilator Y}
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{The Alastor}\\
Cost 8 | Combat 9x2 | Move 1 | Capacity 5 \\
\emph{Sustain Damage}\\
At the start of a space combat, choose any number of your ground forces in this system to participate in that combat as if they were ships.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech} %TODO add

\begin{itemize}
\item \name{UNKNOWN} 
\\
UNKNOWN.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \valefar
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Nekro Malleon}\\
During the action phase, you may exhaust this card to choose a player; that player may discard 1 action card or spend 1 command token from their command sheet to gain 2 trade goods.
\item \name{Commander - Nekro Acidos} \textcolor{gray}{(\emph{Unlock:} Own 3 technologies. A "Valefar Assimilator" technology counts only if its X or Y token is on a technology.)}
After you gain a technology, you may draw an action card.
\item \name{Hero - UNIT.DSGN.FLAYESH / Devour World} \textcolor{gray}{(\emph{Unlock:} UNKNOWN.)}\\
UNKNOWN.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Antivirus}\\
\emph{At the start of a combat:}\\
Place this card faceup in your play area. While this card is in your play area, the Nekro player cannot use his \emph{Technological Singularity} faction ability against you.\\
If you activate a system that contains 1 or more of the Nekro player's units, return this card to the Nekro player.
\end{itemize}

\end{multicols}



