{\handel\Huge The Nomad} \hfill {\Large Difficulty: \easy} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{The Company}\\
During setup, take the 2 additional Nomad agents and place them next to your faction sheet. You control 3 agents during this game.
\item \name{Future Sight}\\
During the agenda phase, after an outcome you voted for or predicted is resolved, gain 1 trade good.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 flagship
\item 1 carrier
\item 1 destroyer
\item 3 fighters
\item 4 infantry
\item 1 space dock
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 4

\vspace{2pt}
\stress{Home System}: Arcturus (4/4)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \sling
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Memoria I}\\
Cost 8 | Combat 7x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
\emph{Anti-Fighter Barrage} 8x3\\
You may treat this unit as if it is adjacent to systems that contain 1 or more of your mechs.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Quantum Manipulator}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
While this unit is in a space area during combat, you may use its \emph{Sustain Damage} ability to cancel a hit that is produced against your ships in this system. 
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \memoriaII
\item \commandSuite
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agents:}
\begin{itemize}
\item \name{Artuno the Betrayer}\\
When you gain trade goods from the supply, you may exhaust this card to place an equal number of trade goods on this card. When this card readies, gain the trade goods on this card.
\item \name{The Thundarian}\\
After the roll dice step of combat, you may exhaust this card. If you do, hits are not assigned to either player's units. Return to the start of this combat round's roll dice step.
\item \name{Field Marshall Mercer}
At the end of a player's turn you may exhaust this card to allow that player to remove up to 2 of their ground forces from the game board and place them on planets they control in the active system.
\end{itemize}
\item \name{Commander - Narvach Feng} \textcolor{gray}{(\emph{Unlock:} Have 1 scored secret objective.)}
You can produce your flagship without spending resources.
\item \name{Hero - Akh-Syl Siven / Probability Matrix} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{Action:} place this card near the game board. Your flagship and units it transports can move out of systems that contain your command tokens during this game round. At the end of this game round, purge this card.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{The Cavalry}\\
\emph{At the start of a space combat against a player other than the nomad:}\\
During this combat, treat 1 of your non-fighter ships as if it had \emph{Sustain Damage}, combat value, and \emph{Anti-Fighter Barrage} value of The Nomad's flagship. Then return this card to The Nomad player at the end of this combat.
\end{itemize}

\end{multicols}



