{\handel\Huge Sardakk N'orr} \hfill {\Large Difficulty: \hard} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Unrelenting}\\
Apply +1 to the result of each of your unit's combat rolls.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 2 carriers
\item 1 cruiser
\item 5 infantry
\item 1 space dock
\item 1 PDS
\color{white}
\item blank
\color{black}
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 3

\vspace{2pt}
\stress{Home System}: 3/2

\rule{\hsize}{0.4pt}\vspace{5pt}

\textcolor{gray}{{\handel\large Starting Technology:} None}

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{C'morran N'orr}\\
Cost 8 | Combat 7x2 | Move 1 | Capacity 5 \\
\emph{Sustain Damage}\\
Apply +1 to the result of each of your other ship's combat rolls in this system.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Valkyrie Exoskeleton}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
After this unit uses its \emph{Sustain Damage} ability during ground combat, it produces 1 hit against your opponent's ground forces on this planet.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Special Units}

\begin{itemize}
\item \exoI
\end{itemize}

%\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \exoII
\item \valkyrie
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - T'ro}\\
\emph{At the end of a player's tactical action:}
\\
You may exhaust this card; if you do, that player may place 2 infantry from their reinforcements on a planet they control in the active system. 
\item \name{Commander - G'hom Sek'kus} \textcolor{gray}{(\emph{Unlock:} Control 5 planets in non-home systems.)}\\
During the commit ground forces step, you can commit up to 1 ground force from each planet in the active system and each planet in adjacent systems that do not contain 1 of your command tokens.
\item \name{Hero - Sh'val, Harbinger / Tekklar Conditioning} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{After you move ships into the active system:}\\
You may skip directly to the ``Commit Ground Forces" step. If you do, after you commit ground forces to land on planets, purge this card and return each of your ships in the active system to your reinforcements.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Tekklar Legion}\\
\emph{At the start of an invasion combat:}\\
Apply +1 to the result of each of your unit's combat rolls during this combat. If your opponent is the N'orr player, apply -1 to the result of each of his unit's combat rolls during this combat.\\
Then return this card to the N'orr player.
\end{itemize}

\end{multicols}



