\newpage
{\handel\Huge The Federation of Sol} \hfill {\Large Difficulty: \hard} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Orbital Drop}\\
\emph{Action:} Spend 1 token from your strategy pool to place 2 infantry from your reinforcements on 1 planet you control.
\item \name{Versatile}\\
When you gain command tokens during the status phase, gain 1 additional command token.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 2 carrier
\item 1 destroyer
\item 3 fighters
\item 5 infantry
\item 1 space dock
\color{white}
\item 1 PDS
\color{black}
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 4

\vspace{2pt}
\stress{Home System}: Jord (4/2)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \neural
\item \antimass
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Genesis}\\
Cost 8 | Combat 5x2 | Move 1 | Capacity 12 \\
\emph{Sustain Damage}\\
At the end of the status phase, place 1 infantry from your reinforcements in this system's space area.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{ZS Thunderbolt M2}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
\emph{Deploy:} After you use the \emph{Orbital Drop} faction ability, you may spend 3 resources to place 1 mech on that planet. 

\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Special Units}

\begin{itemize}
\item \advancedCarrierI
\item \opsI
\end{itemize}

%\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \advancedCarrierII
\item \opsII
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Evelyn Delouis}\\
\emph{At the start of a ground combat round:}\\
You may exhaust this card to choose 1 ground force in the active system; that ground force rolls 1 additional die during this combat round.
\item \name{Commander - Claire Gibson} \textcolor{gray}{(\emph{Unlock:} Control planets that have a combined total of at least 12 resources)}
\emph{At the start of a ground combat on a planet you control:}\\
You may place 1 infantry from your reinforcements on that planet.
\item \name{Hero - Jace X. 4th Air Legion / Helio Command Array} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{Action:} Remove each of your command tokens from the game board and return them to your reinforcements. Then, purge this card.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Military Support}\\
\emph{At the start of the Sol player's turn:}\\
Remove 1 token from the Sol player's strategy pool, if able, and return it to his reinforcements. Then, you may place 2 infantry from your reinforcements on any planet you control.\\
Then return this card to the Sol player.
\end{itemize}

\end{multicols}



