{\handel\Huge The Titans of Ul} \hfill {\Large Difficulty: Unknown} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Terragenesis}\\
After you explore a planet that does not have a sleeper token, you may place or move 1 sleeper token onto that planet.
\item \name{Awaken}\\
After you active a system that contains 1 or more of your sleeper tokens, you may replace each of those tokens with 1 PDS from your reinforcements.
\item \name{Coalescence} If your flagship or your \emph{Awaken} faction ability places your units into the same space area or onto the same planet as another player’s units, your units must participate in combat during the ``Space Combat" or ``Ground Combat" steps. 
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 dreadnought
\item 2 cruiser
\item 2 fighters
\item 3 infantry
\item 1 space dock
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 2

\vspace{2pt}
\stress{Home System}: Elysium (4/1)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \antimass
\item \scanlink
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Ouranos}\\
Cost 8 | Combat 7x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
\emph{Deploy:} After you activate a system that contains 1 or more of your PDS, you may replace 1 of those PDS with this unit.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Hecatoncheires}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
\emph{Deploy:} When you would place a PDS on a planet, you may place 1 mech and 1 infantry on that planet instead.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Special Units}

\begin{itemize}
\item \helTitanI
\item \saturnEngineI
\end{itemize}

%\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \helTitanII
\item \saturnEngineII
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Tellurian}\\
\emph{Action}:\\
\emph{When a hit is produced against a unit:}
\\
You may exhaust this card to cancel that hit. 
\item \name{Commander - Tungstantus} \textcolor{gray}{(\emph{Unlock:} Have 5 structures on the game board)}\\
\emph{When 1 or more of your units use \emph{Production}:}
\\
You may gain 1 trade good. 
\item \name{Hero - Ul The Progenitor / Geoform} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{Action:} Ready Elysium and attach this card to it. Its resource and influence values are each increased by 3, and it gains the SPACE CANNON 5 (x3) ability as if it were a unit.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Terraform}\\
\emph{Action:} Attach this card to a non-home planet you control other than Mecatol Rex. Its resource and influence values are each increased by 1, and it is treated as having all 3 planet traits (cultural, hazardous, and industrial).
\end{itemize}

\end{multicols}



