{\handel\Huge The Winnu} \hfill {\Large Difficulty: \hard} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Blood Ties}\\
You do not have to spend influence to remove the custodians token from Mecatol Rex.
\item \name{Reclamation}\\
After you resolve a tactical action during which you gained control of Mecatol Rex, you may place 1 PDS and 1 space dock from your reinforcements on Mecatol Rex.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 carrier
\item 1 cruiser
\item 2 fighters
\item 2 infantry
\item 1 space dock
\item 1 PDS
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 3

\vspace{2pt}
\stress{Home System}: Winnu (3/4)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \name{Choose any 1 technology that has no prerequisites}.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Salai Sai Corian}\\
Cost 8 | Combat 7 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
When this unit makes a combat roll, it rolls a number of dice equal to the number of your opponent's non-fighter ships in this system.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Reclaimer}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
After you resolve a tactical action during which you gained control of this planet, you may place 1 PDS or 1 space dock from your reinforcements on that planet. 
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \gateFolding
\item \hegemonic
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Berekar Berekon}\\
When 1 or more of a player's units use PRODUCTION, you may exhaust this card to reduce the combined cost of the produced units by 2.
\item \name{Commander - Rickar Rickani} \textcolor{gray}{(\emph{Unlock:} Control Mecatol Rex or enter into a combat in the Mecatol Rex system.)}
During combat, apply +2 to the result of each of your unit's combat rolls in the Mecatol Rex system, your home system, and each system that contains a legendary planet.
\item \name{Hero - Mathis Mathinus} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
\emph{Action:} Perform the primary ability of any strategy card. Then, choose any number of other players. Those players may perform the secondary ability of that strategy card. Then, purge this card. 
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Acquiescence}:\\
\emph{When the Winnu player resolves a strategic action:}\\
You do not have to spend or place a command token to resolve the secondary ability of that strategic card.\\
Then, return this card to the Winnu player.
\end{itemize}

\end{multicols}



