{\handel\Huge The Xxcha Kingdom} \hfill {\Large Difficulty: \easy} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Peace Accords}\\
After you resolve the primary or secondary ability of the ``Diplomacy" strategy card, you may gain control of 1 planet other than Mecatol Rex that does not contain any units and is in a system that is adjacent to a planet you control.
\item \name{Quash}\\
When an agenda is revealed, you may spend 1 token from your strategy pool to discard that agenda and reveal 1 agenda from the top of the deck. Players vote on this agenda instead.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 1 carrier
\item 2 cruisers
\item 3 fighters
\item 4 infantry
\item 1 space dock
\item 1 PDS
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 4

\vspace{2pt}
\stress{Home System}: Archon Ren (2/3); Archon Tau (1/1)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \graviton
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Loncara Ssodu}\\
Cost 8 | Combat 7x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
\emph{Space Cannon} 5x3
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Letani Behemoth}
\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
\emph{Space Cannon} 8\\
You may use this unit's \emph{Space Cannon} ability against ships that are in adjacent systems.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \instinct
\item \nullification
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Ggrocuto Rinn}\\
\emph{Action:}
Exhaust this card to ready any planet; if that planet is in a system that is adjacent to a planet you control, you may remove 1 infantry from that planet and return it to its reinforcements. 
\item \name{Commander - Elder Qanoj} \textcolor{gray}{(\emph{Unlock:} Control planets that have a combined value of at least 12 influence)}\\
Each planet you exhaust to cast votes provides one extra vote.\\
Game effects cannot prevent you from voting on an agenda.
\item \name{Hero - Xxekir Grom / Political Data Nexus} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
When you exhaust planets, combine the values of their resources and influence. Treat the combined value as if it were both resources and influence.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note} %ERRATAD

\begin{itemize}
\item \name{Political Favor}:\\
\emph{When an agenda is revealed:}\\
Remove 1 token from the Xxcha player's strategy pool and return it to his reinforcements. Then, discard the revealed agenda and reveal 1 agenda from the top of the deck. Players vote on this agenda instead.\\
Then, return this card to the Xxcha player.
\end{itemize}

\end{multicols}



