\newpage
{\handel\Huge The Yin Brotherhood} \hfill {\Large Difficulty: \medium} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Indoctrination}\\
At the start of a ground combat, you may spend 2 influence to replace 1 of your opponent's participating infantry with 1 infantry from your reinforcements.
\item \name{Devotion}\\%ERRATAD
After each space battle round, you may destroy 1 of your cruisers or destroyers to produce 1 hit and assign it to 1 of your opponent's ships in that system.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 2 carriers
\item 1 destroyer
\item 4 fighters
\item 4 infantry
\item 1 space dock
\color{white}
\item 1 PDS
\color{black}
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 2

\vspace{2pt}
\stress{Home System}: Darien (4/4)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \sarween
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Van Hauge}\\
Cost 8 | Combat 9x2 | Move 1 | Capacity 3 \\
\emph{Sustain Damage}\\
When this ship is destroyed, destroy all ships in this system.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{Moyin's Ashes}\\
Cost 2 | Combat 6 \\
\emph{Sustain Damage}\\
\emph{Deploy:} When you use your \emph{Indoctrination} faction ability, you may spend 1 additional influence to replace your opponent's infantry with 1 mech instead of 1 infantry. 
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \spinner
\item \impulseCore
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Brother Mil????}\\
UNKNOWN.
\item \name{Commander - Brother Omar} \textcolor{gray}{(\emph{Unlock:} Use your \emph{Indoctrination} faction ability)}
This card satisfies a green technology prerequisite. You may produce one additional infantry for their cost. These infantry do not count against your production limit.
\item \name{Hero - UNKNOWN / UNKNOWN} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
UNKNOWN.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Greyfire Mutagen}:\\
\emph{At the start of a ground combat against 2 or more ground forces that are not controlled by the Yin player:}\\
Replace 1 of your opponent's infantry with 1 infantry from your reinforcements.\\
Then, return this card to the Yin player.
\end{itemize}

\end{multicols}



