{\handel\Huge The Yssaril Tribes} \hfill {\Large Difficulty: \medium} \vspace{-4pt}\\
\hrule width \hsize \kern 1mm \hrule width \hsize height 2pt


\begin{multicols}{2}

\stress{Faction Abilities}

\begin{itemize}
\item \name{Stall Tactics}\\
\emph{Action} Discard 1 action card from your hand.
\item \name{Scheming}\\
When you draw 1 or more action cards, draw 1 additional action card. Then, choose and discard 1 action card from your hand.
\item \name{Crafty}\\
You can have any number of action cards in your hand. Game effects cannot prevent you from using this ability.
\end{itemize}


\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Units}

\vspace{-5pt}
\begin{multicols}{2}
\begin{itemize}
\item 2 carriers
\item 1 cruiser
\item 2 fighters
\item 5 infantry
\item 1 space dock
\item 1 PDS
\end{itemize}
\end{multicols}

\vspace{-5pt}
\stress{Commodities}: 3

\vspace{2pt}
\stress{Home System}: Retillion (2/3); Shalloq (1/2)

\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Starting Technology}

\begin{itemize}
\item \neural
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Flagship}

\begin{itemize}
\item \name{Y'sia Y'ssrila}\\
Cost 8 | Combat 5x2 | Move 2 | Capacity 3 \\
\emph{Sustain Damage}\\
This ship can move through systems that contain other players' ships.
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Mech}

\begin{itemize}
\item \name{UNKNOWN} %TODO add
\\
UNKNOWN
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\nounits

%\rule{\hsize}{0.4pt}\vspace{5pt}
\columnbreak
\stress{Faction Technologies}

\begin{itemize}
\item \transparasteel
\item \mageon
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Leaders}

\begin{itemize}
\item \name{Agent - Ssruu}\\
This card has the text ability of each other player's agent, even if that agent is exhausted. 
\item \name{Commander - UNKNOWN} \textcolor{gray}{(\emph{Unlock:} UNKNOWN)} 
UNKNOWN
\item \name{Hero - UNKNOWN / UNKNOWN} \textcolor{gray}{(\emph{Unlock:} Have 3 scored objectives)}\\
UNKNOWN
\end{itemize}

\vspace{-10pt}\rule{\hsize}{0.4pt}\vspace{5pt}

\stress{Promissory Note}

\begin{itemize}
\item \name{Spy Net}:\\
\emph{At the start of your turn:}\\
Look at the Yssaril player's hand of action cards. Choose 1 of those cards and add it to your hand.\\
Then, return this card to the Yssaril player.
\end{itemize}

\end{multicols}



